\section{Release Plan}

The main features that we intend to implement for iteration 1 of our system is a user based form of access control. Customer users (guests at a hotel) for instance will have two basic forms of access control, anonymous customers and registered customers. Registered customers and anonymous customers will both have the ability to book and unbook rooms; on the other hand, registered customers will simply have the privilege of not having to enter their information every time they wish to book a room where as unregistered customers must do this every time they book a room, also registered customers will have the privilege of being able to unbook rooms where as unregistered customers will have to go through a sales associate. For users employed in the hotel company there are various levels of privilege, administers will have full access to the system as they represent the corporate scheme of the business so they essentially can do everything that all other users can do with the added benefit of adding hotels. Other users types Include Hotel managers, Sales Managers, Room Service Managers, Sales Representatives and Room Service Associates. Customer information access for associates is also intended to be implemented for iteration 1, this includes features such as adding,deleting and modifying customers as well as the ability to create a list of customers in order for an associate to look them up. Most of the above features are concerned with a partial established user control access mechanism that will be used in the future iterations.

The main features intended for iteration 2 of our system include the ability to allow appropriate users to book or unbook rooms, these users include both types of customer users, sales representatives, sales managers, and hotel managers. In order for this feature to work the user types will also have the ability to look for available booking time slots and choose the time slot most appropriate for them. Associates with the proper privileges working for the company will also have the ability of looking up or adding customer information, to select a customer in order to make a booking on that customers behalf. Hotel managers and sales managers will also have the ability of adding and deleting rooms from the hotel booking list in the case of a hotel restructuration. Also for iteration 2 hotel managers and sales managers should be able to deal with adding,deleting and modifying associates who report to them in the employee hierarchy.

The main features intended to be implemented in iteration 3 of our system include the management of customer room service charges and anonymous user access. Customer users will be able to look at their current set of charges, this includes booking prices and rooms service charges. Sales associate, sales managers and hotel managers will also be able to look at a customer's billing status and will also be able to add charges regarding room bookings. Managers will also have the added privilege of removing charges. The room service associates and room service managers will have only the privilege to see charges to the customers room service bills, and the rooms service managers and possibly trusted associates will have the added benefit of removing room service charges from a customer's bill. If possible we may also implement a customer ticket system, where a customer can submit a ticket for complaints, complement and/or suggestions to which certain associates can respond to. Another possible feature which may be included in this iteration is for the ability of administrators to add additional hotels to the system.
