\section{Critical Success Factors}
The hotel manager system must be easy to use, extendible, and scalable. These are
non functional qualities that will aid users to have a better experience with the system, and
developers to be able to easily extend, improve, adapt, and add features to the system without
breaking its main functionality. We will also like to make the webpage scalable so that the hotel
can continue to serve their users better at each stage of their growing process as a company. By
allowing the hotel management website to be able to grow together with the company, we are
also allowing the hotel to take care of their old and new customers so that they can enjoy of all
the amenities and services that the hotel offers in the present and in the future.

The hotel manager website must be easy to use for all the subjects that are going to use
this service. This will initially include both staff and the hotel customers. Although it may be
necessary to have some basic training to place orders, print records, and to perform other admin
activities, we will want to make this as intuitive as possible. This website will certainly need
to improve the effectiveness of the staff involved in performing these operations. Similarly,
we want to make our customers to be able to find and book a room easy and fast. This will be
achieved by focusing early on users and tasks. We will take into consideration and value the
experience of the staff and customers with similar systems, and we will improve it upon that.

Besides making the website easy to use, we believe that in order to be successful we need
to support extensibility of the system. This needs to be done because we are going to be adding
many features on each iteration of the project, and we need to make sure that none of those
features restrict the use of other possible features that we will want to implement at some point.
One of the most important features that we will need to implement in the future is to allow an
anonymous user to browse the contents of our webpage, so that they don?t have the necessity to
provide us with sensitive information if they are just potential customers looking for alternatives.
This should be done at some point because we acknowledge that some people don?t like the idea
of registering for every single thing that they have to do on the internet. Therefore, extensibility
is important because although we have considered these cases, we may not have time to
implement them, but that doesn?t mean that we will compromise the software so that it is forever
static.
