\section{Release Plan}

The purpose of this release plan is to determine and prioritize the set of features that the client desires the system to have, as well as to show the commitment of the team members to each of the project tasks. In this release plane, three main iterations have been identified in total for a single and final product release by April 9th, 2013. The fourth iteration has been set aside as a buffer iteration, that means, that if the workload of an iteration is unbalanced, tasks from iteration 4 will be suggested. These iterations will be approximately three weeks long, and will entail the implementation of different system components.

\subsection{Iteration 1}
Iteration 1 encompases the set of user stories that deal with the bootstrap of project, the partial setup of a User Control Management component and the implementation of the Customer Information Management module.

This iteration will look into the implementation of a user control/access mechanism provided by a Ruby plugin for Registered Customers, Sales Associates, Hotel Managers, and the System Administrator.

Furthermore, at the end of this iteration, both the Hotel Manager and the Sales Associates should be able to access the system and perform create, read, update and delete (CRUD) operations on Customers information. The Admin user type will only be able to maintain system accounts.

\subsection{Iteration 2}
Iteration 2 includes the implementation of the following modules: Hotel Management, Room Management, and the Room Bookings.

In this iteration, the Admin users should be able to perform CRUD operations on Hotels, doing this will allow any user to search for different hotels. The Room Management module, which consists on the CRUD operations on Rooms and Room Types, will be available in this iteration to Hotel Managers, doing this will allow the Sales Associates to see a list of rooms as well.

At the end of this iteration, Sales Associates will be able to book rooms for Customers in the Room Booking module.

\subsection{Iteration 3}
Iteration 3 entails the following modules: Invoicing, Room Service, and Customer self-service.

In the Invoicing module, Sales Associates will be able to record and lookup for customer payments. These payments will also be part of the room service billing history of the customers.

Iteration 3 aims at having Customers to be able to view available rooms, and manage their Room Bookings by themselves. This will require the prior registration of customers to the system in order to perform these tasks. This iteration will conclude the agreed-upon user stories for the project; however, iteration 4 was designed to include some nice-to-have features that could be added to the system if time permits it.

\subsection{Iteration 4}
Iteration 4 which is the buffer iteration will implement a basic Trouble Ticket Management module to address customers inquiries, a Housekeeping module to see the cleanliness of rooms, and a Reporting module for business decisions.

It is important to mention that this release plan is tentative, since the team velocity achieved at each iteration will dictate the amount of tasks to commit to in future iterations. 
